### 2018-03-08 submission/manuscript.Rmd
edit RF section of methods

***Random Forest classification analysis:*** 
To classify individuals as having normal colons or tumors, we built Random Forest classification models for each dataset and comparison using taxa with significant ORs (after multiple comparison correction), all taxa, or OTUs. Because no taxa were identified as having a significant OR associated with adenomas using stool samples or tissue samples, classification models based on OR data were not constructed to classify individuals as having normal colons or adenomas. Within the training dataset, 10-fold cross validation (5-fold cross validation for small datasets) was used to build a model using the default mtry setting that was then evaluated on the testing set. For the models constructed using the taxa with significant ORs, the default mtry setting was used to train the model and this model was tested on the other datasets in the meta-analysis. The reported AUC values are the average AUCs for the application of the model on the test sets. For the OTU-based models, hyperparameters were fit splitting the dataset into training (80% of samples) and testing (20%) sets.  Within the training dataset, 10-fold cross validation was used to identify the best hyperparameters, which were then used to build a model that was then evaluated on the testing set. The original 80/20 split and fitting was repeated 100 times. The Mean Decrease in Accuracy (MDA), a measure of the importance of each taxon to the overall model was used to rank the taxa used in each model.

>>>>

***Random Forest classification analysis:*** 
To classify individuals as having normal colons or tumors, we built Random Forest classification models for each dataset and comparison using taxa with significant ORs (after multiple comparison correction), all taxa, or OTUs. Because no taxa were identified as having a significant OR associated with adenomas using stool samples or tissue samples, classification models based on OR data were not constructed to classify individuals as having normal colons or adenomas. Within the training dataset, 10-fold cross validation (5-fold cross validation for small datasets) was used to build a model using the default mtry setting that was then evaluated on the testing set. For the models constructed using the taxa with significant ORs, the default mtry setting was used to train the model and this model was tested on the other datasets in the meta-analysis. The reported AUC values are the AUCs for the application of the model on the test sets. For the OTU-based models, hyperparameters were fit splitting the dataset into training (80% of samples) and testing (20%) sets.  Within the OTU dataset, 10-fold cross validation (5-fold cross validation for small datasets) was used to identify the best hyperparameters. The original 80/20 split and fitting was repeated 100 times and the average AUC from these 100 repeats was reported. The Mean Decrease in Accuracy (MDA), a measure of the importance of each taxon to the overall model was used to rank the taxa used in each model.

### 2018-03-08 submission/manuscript.tex
edit RF section of methods

\textbf{\emph{Random Forest classification analysis:}} To classify
individuals as having normal colons or tumors, we built Random Forest
classification models for each dataset and comparison using taxa with
significant ORs (after multiple comparison correction), all taxa, or
OTUs. Because no taxa were identified as having a significant OR
associated with adenomas using stool samples or tissue samples,
classification models based on OR data were not constructed to classify
individuals as having normal colons or adenomas. Within the training
dataset, 10-fold cross validation (5-fold cross validation for small
datasets) was used to build a model using the default mtry setting that
was then evaluated on the testing set. For the models constructed using
the taxa with significant ORs, the default mtry setting was used to
train the model and this model was tested on the other datasets in the
meta-analysis. The reported AUC values are the average AUCs for the
application of the model on the test sets. For the OTU-based models,
hyperparameters were fit splitting the dataset into training (80\% of
samples) and testing (20\%) sets. Within the training dataset, 10-fold
cross validation was used to identify the best hyperparameters, which
were then used to build a model that was then evaluated on the testing
set. The original 80/20 split and fitting was repeated 100 times. The
Mean Decrease in Accuracy (MDA), a measure of the importance of each
taxon to the overall model was used to rank the taxa used in each model.

>>>>

\textbf{\emph{Random Forest classification analysis:}} To classify
individuals as having normal colons or tumors, we built Random Forest
classification models for each dataset and comparison using taxa with
significant ORs (after multiple comparison correction), all taxa, or
OTUs. Because no taxa were identified as having a significant OR
associated with adenomas using stool samples or tissue samples,
classification models based on OR data were not constructed to classify
individuals as having normal colons or adenomas. Within the training
dataset, 10-fold cross validation (5-fold cross validation for small
datasets) was used to build a model using the default mtry setting that
was then evaluated on the testing set. For the models constructed using
the taxa with significant ORs, the default mtry setting was used to
train the model and this model was tested on the other datasets in the
meta-analysis. The reported AUC values are the AUCs for the application
of the model on the test sets. For the OTU-based models, hyperparameters
were fit splitting the dataset into training (80\% of samples) and
testing (20\%) sets. Within the OTU dataset, 10-fold cross validation
(5-fold cross validation for small datasets) was used to identify the
best hyperparameters. The original 80/20 split and fitting was repeated
100 times and the average AUC from these 100 repeats was reported. The
Mean Decrease in Accuracy (MDA), a measure of the importance of each
taxon to the overall model was used to rank the taxa used in each model.
